Effects of CHILDREN's programs

### 2020-02-25 paper.Rnw

lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
ts =
td =
lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized 
tss =
tds =

texreg(list(), caption = "Equal Opportunities Regressions", custom.model.names = c())
@

>>>>

lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized 
tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.lm.Rds")
tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")

texreg(list(lm_s, lm_d, ts, td, lm_ss, lm_ds, tss, tds), caption = "Equal Opportunities Regressions", custom.model.names = c("selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills" ))
@

<<ChanceEqualityRegressionsImpute, echo=FALSE, results='asis', message=FALSE>>=

sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.Rds") #standardized
dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") #standardized 
tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds")
tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")

texreg(list(sI, dI, tsI, tdI, ssI, dsI, tssI, tdsI), caption = "Equal Opportunities Regressions, imputed data", custom.model.names = c("selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills" ))
@
